\Large \bf Compilers Project: PTX Super-optimization

### 2018-04-30 paper/main.tex
tried xor, failed

Additionally, the output-by-output processing can be
optimized. Certain outputs are clearly disjoint: finding
one would not aid in finding the other. In theory, by
trying to synthesize all pairs of outputs in either order,
we can determine which outputs are disjoint. This could let
us dramatically reduce the number of candidate programs.
The efficacy of this optimization relies on the idea that
if a pair of outputs is disjoint then one of the outputs
is disjoint to all outputs the other is not disjoint to.
Non-disjointness is best viewed in this usage as an equivalence
relation and disjointness its negation, verifying the above.

@@

From observation, it appears that multiplication is the slowest and most
difficult to process instruction. This may be due to the semantics of the
encoding. For a \texttt{mul.lo.u32 d, x, y;} for instance, the following SAT query
is produced: \texttt{Extract(0 to 32, Zero-Extend(x, 64), Zero-Extend(y, 64)) == d}.
This query may be much slower to process.

>>>>

We call two outputs disjoint if and only if the production of
one does not aid that of the other. The negation of this relation:
two outputs being non-disjoint if the production of one helps the
production of the other is an equivalence relation on the set of outputs.
Hence, we can take equivalence classes of the set of outputs.
Within an equivalence class, the permutation of outputs produced may be
critical, but by definition, the order in which each class is synthesized
does not matter.

We determine disjointness quickly: two outputs are disjoint if and only if
the program that produces them in one order is the same length as that that
produces them in the other order.

Hence, in $o^2$ time, we can know the equivalence classes for $o$ outputs.
This leads to fewer permutations being checked in the synthesis of the entire
program.

@@

From observation, it appears that multiplication is the slowest and most
difficult to process instruction. This may be due to the semantics of the
encoding. For a \texttt{mul.lo.u32 d, x, y;} for instance, the following SAT query
is produced: \texttt{Extract(0 to 32, Zero-Extend(x, 64), Zero-Extend(y, 64)) == d}.
This query may be much slower to process. The test case ``long-mul'' is an example
of this.

The program ``many-classes'' demonstrates how the classes optimization is, indeed,
an optimization with palpable speed-up.

The program ``id'' demonstrates the identities.
